DATA 621 Homework #3

### 2019-10-30 hw3/HW3.Rmd
added in my new feature engineering and tested out some models

@@

@@

>>>>

## Feature Engineering
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(rpart)				        # Popular decision tree algorithm
library(rattle)					# Fancy tree plot
library(rpart.plot)				# Enhanced tree plots
library(RColorBrewer)				# Color selection for fancy tree plot
library(party)					# Alternative decision tree algorithm
library(partykit)				# Convert rpart object to BinaryTree
library(caret)
library(stringr)
library(data.table)
library(plyr);
library(dplyr)
library(randomForest)
library(memisc)
library(plotly)
library(grid)
library(fuzzyjoin)

df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")

density_diff <- function(data,eval_data,var,target,new_column){

data[[paste0(var,"temp")]]<- data[[var]]

eval_data[[paste0(var,"temp")]]<- eval_data[[var]]

#standardize variable between 0 and 1
data[[var]] <- (data[[var]] - min(data[[var]]))/(max(data[[var]]) - min(data[[var]]))

eval_data[[var]] <- (eval_data[[var]] - min(eval_data[[var]]))/(max(eval_data[[var]]) - min(eval_data[[var]]))

## Calculate density estimates
g1 <- ggplot(data, aes(x=data[[var]], group=target, colour=target)) +
  geom_density(data = data) + xlim(min(data[[var]]), max(data[[var]]))
gg1 <- ggplot_build(g1)
# construct the dataset
x <- gg1$data[[1]]$x[gg1$data[[1]]$group == 1]
y1 <- gg1$data[[1]]$y[gg1$data[[1]]$group == 1]
y2 <- gg1$data[[1]]$y[gg1$data[[1]]$group == 2]
df2 <- data.frame(x = x, ymin = pmin(y1, y2), ymax = pmax(y1, y2), 
                  side=(y1<y2), ydiff = y2-y1)
##creating the second graph object
g3 <- ggplot(df2) +
  geom_line(aes(x = x, y = ydiff, colour = side)) +
  geom_area(aes(x = x, y = ydiff, fill = side, alpha = 0.4)) +
  guides(alpha = FALSE, fill = FALSE)

data$join <- data[[var]]
df2$join <- df2$x
temp <- difference_left_join(data,df2, by="join", max_dist =.001)
means <- aggregate(ydiff ~ temp$join.x, temp, mean)

colnames(means) <- c("std_var","density_diff")

new_data <- merge(means,data, by.x ="std_var", by.y =var)
new_data$std_var <- NULL
new_data$join <- NULL
new_data[new_column]<- new_data$density_diff
new_data$density_diff <- NULL
###################same thing with eval data ############################

eval_data$join <- eval_data[[var]]
df2$join <- df2$x
temp <- difference_left_join(eval_data,df2, by="join", max_dist =.001)
means <- aggregate(ydiff ~ temp$join.x, temp, mean)

##new stuff
colnames(means) <- c("std_var","density_diff")
#data["key"] <- (var - min(var))/(max(var) - min(var))

eval_data2 <- merge(means,eval_data, by.x ="std_var", by.y =var)
eval_data2$std_var <- NULL
eval_data2$join <- NULL
eval_data2[new_column]<- eval_data2$density_diff
eval_data2$density_diff <- NULL

eval_data2[[var]] <- eval_data2[[paste0(var,"temp")]]
eval_data2[[paste0(var,"temp")]]<- NULL

new_data[[var]] <- new_data[[paste0(var,"temp")]]
new_data[[paste0(var,"temp")]]<- NULL

mylist <- list(g1,g3,new_data,eval_data2)
names(mylist)<- c("dist","dist_diff","new_data_training","new_data_eval")
return(mylist)

}

```

```{r}
baseline <- glm(target ~ ., family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict(baseline, test) < 0.5, 0, 1)
test$baseline_yhat <- predict(baseline, test)
confusionMatrix(factor(test$baseline), factor(test$target))
```

#Creating Some New Variables

```{r}
str(train)
str(test)
## try it out 
train <- density_diff(train,test,"nox",train$target,"nox_density")$new_data_training
train <- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
train <- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
train <- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
train <- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
train <- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
train <- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
train <- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
train <- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training

test<- density_diff(train,test,"nox",train$target,"nox_density")$new_data_eval
test<- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
test<- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
test<- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
test<- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
test<- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
test<- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
test<- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
test<- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training

str(train)
str(test)

```

@@

```{r}

density_models <- glm(target ~ nox_density +indus_density+age_density+dis_density+rad_density+tax_density+ptratio_density+lstat_density+medv_density, family = binomial(link = "logit"), train)
summary(density_models)
test$density_models <- ifelse(predict(density_models, test) < 0.5, 0, 1)
test$density_models_yhat <- predict(density_models, test)
confusionMatrix(factor(test$density_models), factor(test$target))
```

@@

## pROC Output

```{r}
library(pROC)
par(pty = "s")
roc(test[["target"]], test[["density_models_yhat"]], plot = TRUE, legacy.axes = TRUE, print.auc = TRUE)
par(pty = "m")

library(pROC)
par(pty = "s")
roc(test[["target"]], test[["model2_yhat"]], plot = TRUE, legacy.axes = TRUE, print.auc = TRUE)
par(pty = "m")

library(pROC)
par(pty = "s")
roc(test[["target"]], test[["model1_yhat"]], plot = TRUE, legacy.axes = TRUE, print.auc = TRUE)
par(pty = "m")
```
